---
title: Stops
runningheader: "Police Stops"
author: notes
date: "`r Sys.Date()`"
documentclass: book
bibliography: "`r file.path(getwd(), 'bibliography', 'bibliography.bib')`"
csl: "`r file.path(getwd(), 'bibliography', 'cambridge-university-press-numeric.csl')`"
link-citations: yes
classoption:
  - fleqn
extra_dependencies:
  - float
site: bookdown::bookdown_site
output: bookdown::tufte_book2
---



<!--- Global Settings --->
```{r include = FALSE}
# Settings
knitr::opts_chunk$set(echo = FALSE, comment = '')
options(knitr.table.format = 'latex')
options(knitr.kable.NA = '')
# Invalidate cache when the tufte version changes
library(tufte)
knitr::opts_chunk$set(cache.extra = packageVersion(pkg = 'tufte'))
options(htmltools.dir.version = FALSE)
```


```{r include = FALSE}
library(xtable)
library(ggplot2)
library(dplyr)
library(tidyr)
library(stringr)
library(magrittr)
library(latex2exp)
library(patchwork)
library(knitr)
library(kableExtra)
library(tmap)
library(sf)
```

<!--- settings --->
```{r exploration settings}
pathstr <- dirname(getwd())
```



# *INTRODUCTION* {-}

A brief re-visit of generalised linear models, focusing on count outcomes.


# *THE CASE*

The focus herein is an analysis of police stops in New York.  Let $y_{i}$ denote the number of police stops in a New York precinct vis-à-vis an ethnic group. The data focuses on the same $3$ ethnic groups per precinct. There are $75$ precincts, hence $225$ observations, i.e., $i = {1, 2, \ldots, 225}$.  In addition to the precinct and ethnic group variables, the data includes the number of past arrests per precinct/ethnicity combination.

The stops are counts, hence analysis is via Poisson models.  In general

\begin{equation}
y_{i} \sim Poisson(\mathcal{u}_i \lambda_{i}) (\#eq:0001)
\end{equation}

whereby

\begin{equation}
\lambda_{i} = exp(\mathbf{x}_{i} \mathbf{\beta}) (\#eq:0002)
\end{equation}

hence

\begin{equation}
ln(\mathcal{u}_i \lambda_{i}) = ln(\mathcal{u}_i) + \mathbf{x}_{i} \mathbf{\beta} (\#eq:0003)
\end{equation}

